Drake Plan

### 2019-12-22 R/drake_plan_conus.Rmd
update path to Just_universal

suppressPackageStartupMessages({
  library(sf)
  library(magrittr)
  library(drake)
  library(data.table)
  library(fst)
  library(future)
  library(here)
  library(nngeo)
  library(ggplot2)
  library(SHAPforxgboost)
})
# ** need to revise accordingly the path to your local clone of Just_universal **
source("~/liuyanguu/Just_universal/code/xgboost_cvtune.R")
source("~/liuyanguu/Just_universal/code/xgboost_cv_RFE.R")

>>>>

suppressPackageStartupMessages({
  library(sf)
  library(magrittr)
  library(drake)
  library(data.table)
  library(fst)
  library(future)
  library(here)
  library(nngeo)
  library(ggplot2)
  library(SHAPforxgboost)
})
# ** need to revise accordingly the path to your local clone of Just_universal **
source(here("../Just_universal/code/xgboost_cvtune.R"))
source(here("../Just_universal/code/xgboost_cv_RFE.R"))
